---
title: "2023_03_02_Lab_Homework"
author: "Cindy Fajardo"
date: "`r Sys.Date()`"
output: hrbrthemes::ipsum
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.path = "../Output/")
```
# Welcome
*Hello* and welcome to my super awesome R markdown. In this file you will find

-  **Plot of Chemical Data**
-  **Table of Averaged Values per Variable in Chemical Data**

I hope you find my page fun and interesting. _Toodles_

# Load Libraries
Loading libraries that I need to make my beautiful graph and table
```{r}
knitr::opts_chunk$set(message = FALSE)
library(here)
library(tidyverse)
library(palmerpenguins)
library(lubridate)
library(devtools)
library(kableExtra)
library(memer)
```

# Chemical Data Plot
I decided to make a facet wrapped box plots of the Chemical data. The plot describes the all of the values of the different variables collected separated by seasons.
```{r Homework plot}
ChemData <- read_csv(here("Week_04","Data","chemicaldata_maunalua.csv")) #read data in
ChemData_long <- ChemData %>% #name chem data
  drop_na() %>% #drop na's
  pivot_longer(cols = Temp_in:percent_sgd, #pivot long
               names_to = "Variables", #give name to new column with variable names
               values_to = "Values") %>% # give name to column with values
  select(Site, Season, Variables, Values) #select data I want

ggplot(ChemData_long, #datframe used
       aes(x = Season, #x axis
           y = Values, #y axis
           color = Season))+ #color by season
  geom_boxplot()+ #box plot
  facet_wrap(~Variables, scales = "free")+ #facet wrap box plot
  theme_dark()+ #dark background
  labs(title = "Values of Different Varibales Across Two Seasons") #labels
```

# Chemical Data Table
In this section I have listed a table of all of the average values for all of the variables 
```{r Homework Table}
ChemData_long %>% #use long chem data I made
  group_by(Variables) %>% # group by variable
  summarise(Average_values = mean(Values, na.rm = TRUE)) %>% #summarise all values for variables
  kbl(caption = "Averaged Values per Variable") %>% #add title to table
  kable_styling(full_width = FALSE) %>% #make table smaller
  row_spec(c(1,3,5,7), background = "pink")# make it a kable table #add color to every other row
```

