---
title: "2023_04_25_Lab_HW"
author: "Cindy Fajardo"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      fig.path = "../Output/")
```

# Lab
You have a set of 4 .csv files in data/homework. Each of these files is a timeseries of temperature and light data collected in tide pools in Oregon by Jenn Fields. Your goal is to bring in all 4 files and calculate the mean and standard deviation of both temperature (Temp.C) and light (Intensity.lux) for each tide pool. Use both a for loop and map() functions in your script. (Basically, do it twice). Due Tuesday at 1pm.

# Libraries
```{r}
library(tidyverse)
library(here)
```


# For Loops
```{r}
# point to the location on the computer of the folder
hwPath<-here("Week_12", "Data", "homework")
files <- dir(path = hwPath,pattern = ".csv")
files

# pre-allocate space
# make an empty dataframe that has one row for each file and 5 columns
homework<-data.frame(matrix(nrow = length(files), ncol = 5))
# give the dataframe column names
colnames(homework)<-c("filename","mean_temp", "stdev_temp", "mean_light", "stdev_light")
homework

raw_data<-read_csv(paste0(hwPath,"/",files[1])) # test by reading in the first file and see if it works
head(raw_data)
mean_temp<-mean(raw_data$Temp.C, na.rm = TRUE) # calculate a mean
mean_temp
stdev_temp <- sd(raw_data$Temp.C, na.rm = TRUE) # calculate standard deviation 
stdev_temp

for (i in 1:length(files)){ # loop over 1:4 the number of files 
raw_data<-read_csv(paste0(hwPath,"/",files[i])) # read in all (i) files
#glimpse(raw_data)
homework$filename[i]<-files[i] # providing info for column
homework$mean_temp[i]<-mean(raw_data$Temp.C, na.rm =TRUE) # providing mean for column
homework$stdev_temp[i]<-sd(raw_data$Temp.C, na.rm =TRUE) # providing sd for column
homework$mean_light[i] <- mean(raw_data$Intensity.lux, na.rm = TRUE) # providing mean for column
homework$stdev_light[i] <- sd(raw_data$Intensity.lux, na.rm = TRUE) # providing sd for column
} 
homework
```

# Maps
```{r}
# point to the location on the computer of the folder
hwPath<-here("Week_12", "Data", "homework")
files <- dir(path = hwPath,pattern = ".csv", full.names = TRUE) #have to set full.names = TRUE so that R can look in the correct folder when looking for file names
files

#Next, read in the files using map instead of a for loop while retaining the filename as a column.
hwdata<-files %>%
  set_names()%>% # set's the id of each list to the file name
  map_df(read_csv,.id = "filename") %>% # map everything to a dataframe and put the id in a column called filename
  group_by(filename) %>%
  summarise(mean_temp = mean(Temp.C, na.rm = TRUE),
            stdev_temp = sd(Temp.C,na.rm = TRUE),
            mean_light = mean(Intensity.lux, na.rm = TRUE),
            stdev_light = sd(Intensity.lux, na.rm = TRUE)) %>% 
  mutate(filename = str_sub(filename, start = -7, end = -1))
hwdata
```

