---
title: "2023_04_20_Lecture_notes"
author: "Cindy Fajardo"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries
```{r, Libraries}
library(tidyverse)
library(here)
```

# Load Data
```{r}
income_mean <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-02-09/income_mean.csv')
```

# What is a factor
```{r}
fruits<-factor(c("Apple", "Grape", "Banana"))
fruits
```

# factor booby-traps!
```{r}
test<-c("A", "1", "2")
as.numeric(test)
test<-factor(test) # covert to factor
as.numeric(test)
```
# Forecats Starwars
```{r, starwars}
starwars %>% 
  filter(!is.na(species)) %>% # remove the NAs
  count(species, sort = TRUE)
star_counts<-starwars %>%
  filter(!is.na(species)) %>%
  mutate(species = fct_lump(species, n = 3)) %>%
  count(species)

star_counts

star_counts %>%
  ggplot(aes(x = species, y = n))+
  geom_col()
```

# reordering factors
```{r}
star_counts %>%
  ggplot(aes(x = fct_reorder(species, n), y = n))+ # reorder the factor of species by n
  geom_col()

star_counts %>%
  ggplot(aes(x = fct_reorder(species, n, .desc = TRUE), y = n))+ # reorder the factor of species by n in descending order
  geom_col() +
  labs(x = "Species")
```

# We will make a plot of the total income by year and quantile across all dollar types.
```{r}
total_income<-income_mean %>%
  group_by(year, income_quintile)%>%
  summarise(income_dollars_sum = sum(income_dollars))%>%
  mutate(income_quintile = factor(income_quintile)) # make it a factor

total_income%>%
ggplot(aes(x = year, y = income_dollars_sum, color = income_quintile))+
  geom_line()

#We can reorder line plots by using fct_reorder2, which reorders the data by two variables
total_income%>%
  ggplot(aes(x = year, y = income_dollars_sum, 
             color = fct_reorder2(income_quintile,year,income_dollars_sum)))+
  geom_line()+
  labs(color = "income quantile")
```

# reorder levels directly in a vector because I said so
```{r}
x1 <- factor(c("Jan", "Mar", "Apr", "Dec"))
x1

#This order is probably not what we want... You can set the specific order of the levels
x1 <- factor(c("Jan", "Mar", "Apr", "Dec"), levels = c("Jan", "Mar", "Apr", "Dec"))
x1
```

# subest data with factors
Back to starwars. Let's say we instead of grouping our species that have < 3 counts into "Other" we just filter them out.
```{r}
starwars_clean<-starwars %>% 
  filter(!is.na(species)) %>% # remove the NAs
  count(species, sort = TRUE) %>%
  mutate(species = factor(species)) %>% # make species a factor
  filter(n>3) %>% # drop extra levels# only keep species that have more than 3
  droplevels() 
starwars_clean

# Check the levels of the factor
levels(starwars_clean$species)
```

# recode levels
If you want to rename (or recode) a level. For example, lets recode Human to Humanoid.
```{r}
starwars_clean<-starwars %>% 
  filter(!is.na(species)) %>% # remove the NAs
  count(species, sort = TRUE) %>%
  mutate(species = factor(species)) %>% # make species a factor 
  filter(n>3)  %>% # only keep species that have more than 3 
  droplevels() %>% # drop extra levels 
  mutate(species = fct_recode(species, "Humanoid" = "Human")) # this renames
starwars_clean
```

