---
title: "2023_03_09 Intro to Google Maps"
author: "Cindy Fajardo"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    theme: darkly
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      fig.path = "../Output/")
```

# Load Libraries
```{r Libraries}
library(ggmap)
library(tidyverse)
library(here)
library(ggsn)
library(emojifont)
```

# Load Data

```{r Chemical Data}
ChemData<-read_csv(here("Week_07","Data","chemicaldata_maunalua.csv"))
glimpse(ChemData)
```
# Get base maps from ggmap

get_map() is the function to get a basemap from Google Maps. At it's simplest form, you only need to put in a location.
Use ggmap to plot the base layer

```{r Oahu}
register_google(key = "AIzaSyDy4dZ675IcOI8hIqCsoWeV8E4QYVSfduI")
Oahu<-get_map("Oahu")
ggmap(Oahu)

geocode("California")
CA<-data.frame(lon = -119.4179, lat = 36.77826)
Cali<-get_map(CA)
ggmap(Cali)
```
# Get coordinates for Wailupe on Oahu

You can also put in lat and lon coordinates to get a basemap.

```{r Get Map}
#Make a data frame of lon and lat coordinates
WP<-data.frame(lon = -157.7621, lat = 21.27427) # coordinates for Wailupe
# Get base layer
Map1<-get_map(WP)
# plot it
ggmap(Map1)
```
# Zoom in on a location

The _zoom_ argument, an integer from **3** to **20** specifying how large the spatial extent should be around the center, with 3 being the **continent** level and 20 being roughly the **single building level**.

```{r Zoomed Map}
Map1<-get_map(WP,zoom = 17)
ggmap(Map1)
```
# Change the map type

```{r Satellite Map}
Map1<-get_map(WP,zoom = 17, maptype = "satellite")
ggmap(Map1)
Map1<-get_map(WP,zoom = 17, maptype = "watercolor")
ggmap(Map1)

```
# You can use the ggmap base layer in any ggplot

```{r Base Layer Map}
Map1<-get_map(WP,zoom = 17, maptype = "satellite") 
ggmap(Map1)+
  geom_point(data = ChemData,
             aes(x = Long, y = Lat, color = Salinity),
             size = 4) +
  scale_color_viridis_c()
```
# Add scale bar

```{r Scale Bar}
ggmap(Map1)+
  geom_point(data = ChemData, 
             aes(x = Long, y = Lat, color = Salinity), 
             size = 4) + 
  scale_color_viridis_c()+
  scalebar( x.min = -157.766, x.max = -157.758, #tells where to put bar on x axis
           y.min = 21.2715, y.max = 21.2785, #tells where to put bar n y axis
            dist = 250, #show distance so 0-250
           dist_unit = "m", #units we want to show distance
           model = "WGS84", #specific to gps model you are working with
            transform = TRUE, st.color = "pink",
            box.fill = c("yellow", "white"))
```
# Don't know the exact lat and long?

Use geocode() to get exact locations that you can then use in the maps.

```{r Geocode}
geocode("the white house") #gets long and lat of white house
geocode("California State University, Northridge") #gets lat and long of center of csun
```

