---
title: "Map of Meteorites"
author: "Cindy Fajardo"
date: "`r Sys.Date()`"
output: rmdformats::material
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.path = "../Output/")
```
# Welcome
Hello, and welcome to this weeks R Markdown file. This week will include a really cool map of meteorites. Hope you enjoy!

# Load Libraries
Load libraries that I need to make my beautiful map
```{r}
library(here)
library(tidyverse)
library(palmerpenguins)
library(lubridate)
library(devtools)
library(kableExtra)
library(memer)
library(maps)
library(mapproj)
library(mapdata)
```

# Get the data
readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-06-11/meteorites.csv")
```{r Bring in Data}
meteorites <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-06-11/meteorites.csv") %>% #read in data from Github
  select(fall, year, lat, long) %>% #select columns I want to work with
  filter(year > 1912, #filtered to get 100 years of data
         fall == "Fell") #wanted meteorites that fell, not found


#Data from USA
usa<-map_data("usa") #used usa map
state <- map_data("state") #used states of usa map for map
```
# Map
I used the meteorite data to make a map of the United states that show fallen meteorites from 1913-2013. I was attempting to filter out longitude and latitude in the meteorite data to make my picture bigger but I was having a hard time, so this is what I got, and I am happy with it. 
```{r Homework Map, out.width="125%"}
ggplot()+
  geom_polygon(data = state, #used state to get state lines drawn on US
               aes(x = long, 
                   y = lat, 
                   group = group,
                   fill = region),  #used fill to make stte lines
               color = "black")+
   geom_point(data = meteorites, # add a point at all my sites 
             aes(x = long, 
                 y = lat))+
    guides(fill=FALSE)+ #removed guide of states
  coord_map(projection = "mercator",
            xlim = c(-125, -20), #set longitude
            ylim = c(25, 48))+ #set latitude
  theme_void()+ #only show US, not gridlines
  labs(title = "Sites of Fallen Meteorites in USA Over 100 Years (1913-2013)")
```

